---
title: "Elliott is Awesome"
author:
  - Elliott Hazen:
      email: ehazen@stanford.edu
      institute: [Stanford]
      correspondence: true
  - Yourfirstname Yourlastname:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/nature.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

<!-- The actual document text starts here: -->

# Introduction

Here is a citation [@Marwick2017]

# Background

# Methods

# Results

```{r load}
        library(maxspeed)   # Cmd-shift-B
        library(dplyr)
        library(ggplot2)
        maxspeed <- readRDS("../data/derived_data/maxspeed.RDS")
```

```{r function}
#' Fit time-dependent maximum speed model
#'
#' @param dat `[data.frame]` Subset of the maximum speed database. Requires columns `max_spd_kmh` and `mass_kg`.
#'
#' @return `[nls]` A fitted non-linear regression model.
#' @export
fit_maxspeed <- function(dat) {
  # Numerical methods sometimes fail to fit the model, so just keep trying until
  # it works
  tryCatch({
    stats::nls(
      formula = max_spd_kmh ~ a * mass_kg^b * (1 - exp(-h * mass_kg^i)),
      data = dat,
      start = list(a = runif(1, 11.2 - 0.91, 142.8 + 16.7),
                   b = runif(1, 0.24 - 0.01, 0.36 + 0.02),
                   h = runif(1, 2.4 - 1.4, 19.5 + 13.6),
                   i = runif(1, -0.72 - 0.26, -0.56 + 0.07))
    )},
    error = function(e) fit_maxspeed(dat)
  )
}


#' Maximum speed predictions
#'
#' @param mass_kg `[numeric]` Mass of animals for model prediction (in kg)
#' @param mod `[nls]` A fitted time-dependent maximum speed model (see `fit_maxspeed()`)
#'
#' @return `[numeric]` Predicted maximum speeds for animals of size `mass_kg`
#' @export
predict_maxspeed <- function(mass_kg, mod) {
  stats::predict(mod, newdata = data.frame(mass_kg = mass_kg))
}

```


<!-- Here's some example analysis code: -->

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
####  my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
```

```{r demo-plot, fig.cap="A plot of random numbers"}
plot(rnorm(10))
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r demo-inline-code}
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence. 

# Figure 2a

```{r fig2a}
        palette <- list(green = "#83CE3D",
                        orange = "#E39F2F",
                        blue = "#5F9FA1")

        fly_dat <- filter(maxspeed, locomotion == "flying")
        fly_model <- fit_maxspeed(fly_dat)
        fly_spd <- tibble(
          mass_kg = seq(min(fly_dat$mass_kg), max(fly_dat$mass_kg), length.out = 1000),
          max_spd_kmh = predict_maxspeed(mass_kg, fly_model)
        )

        run_dat <- filter(maxspeed, locomotion == "running")
        run_model <- fit_maxspeed(run_dat)
        run_spd <- tibble(
          mass_kg = seq(min(run_dat$mass_kg), max(run_dat$mass_kg), length.out = 1000),
          max_spd_kmh = predict_maxspeed(mass_kg, run_model)
        )

        swm_dat <- filter(maxspeed, locomotion == "swimming")
        swm_model <- fit_maxspeed(swm_dat)
        swm_spd <- tibble(
          mass_kg = seq(min(swm_dat$mass_kg), max(swm_dat$mass_kg), length.out = 1000),
          max_spd_kmh = predict_maxspeed(mass_kg, swm_model)
        )

        ggplot(fly_dat, aes(x = mass_kg, y = max_spd_kmh)) +
          geom_point(color = palette$green, size = 0.5, shape = 15) +
          geom_point(data = run_dat, color = palette$orange, size = 0.5, shape = 16) +
          geom_point(data = swm_dat, color = palette$blue, size = 0.5, shape = 17) +
          geom_line(data = fly_spd, 
                    color = palette$green, 
                    size = 1.25) +
          geom_line(data = fly_spd, 
                    color = "white", 
                    size = 0.5) +
          geom_line(data = run_spd, 
                    color = palette$orange, 
                    size = 1.25) +
          geom_line(data = run_spd, 
                    color = "white", 
                    size = 0.5) +
          geom_line(data = swm_spd, 
                    color = palette$blue, 
                    size = 1.25) +
          geom_line(data = swm_spd, 
                    color = "white", 
                    size = 0.5) +
          scale_x_log10("Body mass (kg)",
                        limits = 10^c(-10, 7),
                        breaks = 10^c(-10, -6, -2, 1, 4, 7),
                        labels = scales::trans_format("log10", scales::math_format(10^.x))) +
          scale_y_log10(bquote(Speed~(km~h^-1)),
                        limits = 10^c(-2, 3),
                        breaks = 10^(-2:3),
                        labels = c("0.01", "0.1", "1", "10", "100", "1,000")) +
          annotation_logticks() +
          theme_classic() +
          theme(aspect.ratio = 1)
```
# Discussion

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break  -->

\newpage

# References 

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

<div id="refs"></div>

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies: 

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
